The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
work paragraph 1 habitat selection

## Habitat selection and space use
<!--
* Social structure is influenced by large scale processes such as resource availability and seasonality [@Peigner_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
* Habitat selection definition
* johnson's four scales of selection and Mayor 2009 habitat selection across scales
* habitat selection influences social structure since resource availability + quality influence home range size and overlap
* individuals must share space to interact [@Farine_2015]
* multilayer networks represent a novel framework for considering habitat selection and space use on sociality across scales

individual differences in habitat selection
-->

Social structure influenced by large scale processes, eg resources
Animals select for these same processes, habitat selection, as measured by RSF
All of these processes are influenced by scale: 
RSFs are are influenced
Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered
sociality across scales of sociality + temporal and spatial as shown above
ML networks present a framework for this

Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
available" [@Mayor_2009] landscape resources or features by animals. Combined, habitat selection and social structure are intimately linked as
individuals must share space to interact [@Farine_2015] and resource
availability and quality influence home range size and overlap. Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.
 Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.

@@

With our caribou case stuyd, we show that (1) multilayer social networks can be,
but are not always, scale dependent and (2) that the use of multilayer networks
could be useful for identifying habitat or season-specific social processes. Our
analyses of social, spatial, and temporal scales in multilayer network framework
highlight potential to identify scales at which variation in properties of
layers within a multilayer network show the most variability. Our analysis of
caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data, thus allowing us ground our broader discussion of
multilayer networks in the context of observed animal social networks.
<!--QW: I am not very happy with this paragraph, but it's a start -->

Multilayer networks remain a nascent tool in animal behavioural ecology. We
demonstrate novel analyses that vary social, spatial, and temporal scale within
a multilayer framework and we discuss the potential integration of individual
phenotypes and fitness, collective movememtn, and habitat selection for future
analyses considering spatial ecology  using multilayer networks. Silk et al.
(2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:

>>>>

## Habitat selection and space use
Animals use space for resource, considering conspecifics

social structure is influenced by resources

animals selectively use resources + can be measured by RSFs

<!-- Social structure influenced by large scale processes, eg resources -->
<!-- Animals select for these same processes, habitat selection, as measured by RSF -->
<!-- All of these processes are influenced by scale:  -->
<!-- RSFs are are influenced -->
<!-- Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered -->
<!-- sociality across scales of sociality + temporal and spatial as shown above -->
<!-- ML networks present a framework for this -->

<!-- TODO: Gerard ‘openness’ paper -->
Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
available resources or features by animals [@Manly_1993; @Boyce_1999]. Combined,
social structure and habitat selection are intimately linked as individuals must
share space to interact and distribution of resources influence home range size
and group dynamics [@Webber_2018]. <!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.

Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.

@@

Multilayer networks remain a nascent but powerful tool in animal behavioural ecology. We
demonstrate novel analyses that vary social, spatial, and temporal scale within
a multilayer framework. In our caribou case study, we show that (1) multilayer social networks can be,
but are not always, scale dependent, and (2) the use of multilayer networks
could be useful for identifying habitat or season-specific social processes. Our
analyses of social, spatial, and temporal scales in multilayer network framework
highlight potential to identify scales at which different properties of
layers within a multilayer network show the most variability. Furthermore, we discuss the potential integration of individual phenotypes and fitness, collective movement, and habitat selection for future
analyses considering spatial ecology  using multilayer networks.

<!--QW: I am not very happy with this paragraph, but it's a start -->
Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement. 
Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.

Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:
